\Large\bf FlexibleSUSY --- A spectrum generator generator for supersymmetric models

### 2014-06-06 doc/paper.tex
e.g, --> e.g.~ in introduction.

None of the fundamental motivations of supersymmetry require
minimality, and specific alternatives to (or extensions of) the MSSM
are, for example, motivated by the $\mu$-problem of the
MSSM \cite{Kim:1983dt}; explaining the family structure (see e.g,
\cite{King:2014nza}) or for successful baryogenesis or leptogenesis
(see e.g,\cite{King:2008qb}). However constructing specialized tools
to study all relevant models would require an enormous amount of work.
So general tools which can automate this process and produce fast and
reliable programs can greatly enhance our ability to understand and
test non-minimal realizations of supersymmetry.

>>>>

None of the fundamental motivations of supersymmetry require
minimality, and specific alternatives to (or extensions of) the MSSM
are, for example, motivated by the $\mu$-problem of the
MSSM \cite{Kim:1983dt}; explaining the family structure (see e.g.~\cite{King:2014nza}) or for successful baryogenesis or leptogenesis
(see e.g.~\cite{King:2008qb}). However constructing specialized tools
to study all relevant models would require an enormous amount of work.
So general tools which can automate this process and produce fast and
reliable programs can greatly enhance our ability to understand and
test non-minimal realizations of supersymmetry.
